Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''

### 2019-05-15 tex/v3/section_1_introduction.tex
new modif of tex

Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures.
The proposed approach is based on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,nocedal2006numerical} that relies on an estimation of the inverse of the Hessian based on gradients differences. 
L-BFGS-B algorithm was adapted to the the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.

>>>>

Our focus in this paper is a new analysis of Sinkhorn algorithm for approximating regularized OT distance between discrete measures.
The proposed approach is based on reformulating the dual of Sinkhorn divergence by adding new constraints feasibility.
These constraints are defined through a convex set which depends on two parameters acting like threshold and scaling factor.
We prove that dual solution of this reformulation guarantees the existence of two active indices sets for the potential variables.
Furthermore, the active sets are both directly linked to a priori fixed number budget of points from the supports of the given discrete measures.
We then restrict the constraints feasibility by taking into account the properties providing by the active sets to get a ``screened'' version of the dual of Sinkhorn divergence. 
Screenkhorn algorithm developed in this paper consists of two steps; the first one is an initialization step devoted to determine the active sets while the second is a constrained L-BFGS-B solver, a limited-memory quasi-Newton algorithm~\cite{nocedal1980,byrd1995L-BFGS-B} that relies on an estimation of the inverse of the Hessian based on gradients differences. 
L-BFGS-B algorithm was adapted to the OT setting via the dual of Sinkhorn divergence in ~\cite{cuturi2016SIAM,blondel2018ICML}.

### 2019-05-15 tex/v3/section_3_algorithm.tex
new modif of tex

% In this section we describe the main algorithm studied in this paper. 
For a fixed $\varepsilon > 0$ and $\kappa > 0$ we define an \emph{approximate dual of Sinkhorn divergence} as follows:
\begin{equation} 
\label{screen-sinkhorn}
\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
\end{equation}
where $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, is a convex set  given by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.

The objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, then the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
The $\kappa$-parameter plays a role of scaling factor, namely it allows to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for $e^u$ and $e^v$.
Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
The screening procedure presented in this work is based on constructing two {active sets} $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} in the following way:

@@

First order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$ 
which correspond to the Sinkhorn marginal conditions up to the scaling factor $\kappa$.

@@

Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$. 
The explicit determination of its values depends on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$. % in problem~\eqref{screen-sinkhorn}.  
In the sequel of the paper, we denote by $n_b \in\{1, \ldots, n\}$ and the $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}.

Let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
\begin{equation}
\label{epsilon_kappa}
 \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
\end{equation}
Note that $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$. 
Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.

Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ in problem~\eqref{screen-sinkhorn} to the screened domain $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where 
\begin{equation*}
\mathcal{U}_{\text{sc}} = \{u \in \R^n: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
\end{equation*}
and 
\begin{equation*}
	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
\end{equation*}
where the vector comparison $\succeq$ has to be understood elementwise.
Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as 
\begin{align}
\label{screen-sinkhorn_second_def}
\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
\end{align}
where 
\begin{align*} 
\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
\end{align*}
with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.

Pseudocode of our proposed algorithm is given in Algorithm~\ref{screenkhorn}.
Screenkhorn consists of two steps: the first one is an initialization where we calculate the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained L-BFGS solver~\cite{zhu1997-LBFGS} for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
% It is worth to note that the couple variables $(u,v)$ to be optimized in Screenkhorn belongs to $\R^{n_b\times m_b}$. 
It is worth to note that Screenkhorn uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$

The following lemma expresses upper and lower bounds to be respected in Screenkhorn.
\begin{lemma}
\label{lemma_bounds_of_usc_and_vsc}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}. Then,
one has
\begin{equation}
\label{bound_on_u}
\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa\min_{i,j}K_{ij}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}},
\end{equation}
and
\begin{equation}
\label{bound_on_v}
\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon\min_{i,j}K_{ij}} n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\min_{i,j}K_{ij}}
\end{equation}
for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
\end{lemma}

@@

\nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}

\textbf{step 2:} \textcolor{black}{L-BFGS}\\

\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
\nl   $\theta \gets \text{L-BFGS}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\

>>>>

\begin{wrapfigure}{o}{0.44\textwidth}
\vspace{-15pt}
\centering
\includegraphics[width=0.4\textwidth]{./figs/motivations.pdf}%, height=0.2\textwidth
\caption{Plotting of $e^{u^\star}, e^{v^\star}$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual}.}
\label{fig:motivations}
\vspace{-15pt}
\end{wrapfigure}

\paragraph{Motivation.} The key idea of our approach comes from the so-called \emph{static screening test}~\cite{Ghaoui2010SafeFE} in supervised learning, a method is able to quickly identify inactive features, i.e., features that have zero components in the solution vector. 
Then, these inactive features can be removed from the optimization problem to reduce its scale.
Before diving into detailed algorithmic analysis, let's us present a brief illustration of how we adapt static screening test to the dual of Sinkhorn divergence.
Towards this end, we define the convex set $\mathcal{C}^r_{\alpha} \subseteq \R^r$, for $r\in \mathbb N$ and $\alpha >0$, by $\mathcal{C}^r_{\alpha} = \{w \in \R^{r}: \min_{1\leq i\leq r} e^{w_i} \geq \alpha\}$.
In Figure~\ref{fig:motivations}, we plot $(e^{u^\star}, e^{v^\star})$ solution of dual of Sinkhorn divergence~\ref{sinkhorn-dual} in the particular case of: $n=m=500, \eta=0.1, \mu = \nu = \frac 1n \mathbf 1_n$ and the cost matrix $C$ correspond the pairwise euclidean distance, i.e., $C_{ij} = \norm{x_i - y_j}_2$. % \nu = \frac 1m \mathbf 1_m
We also plot two lines correspond to $e^{u^\star} \equiv \alpha_u$ and $e^{v^\star} \equiv \alpha_v$ for some $\alpha_u>0$ and $\alpha_v >0$, playing the role of thresholds to select indices to be discard from the optimization procedure.

\paragraph{Static screening test.} The core of the static screening test developed in this work aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and 
$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
The sets $I$ and $J$ will be called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.

In the following, the parameters $\alpha_u = \varepsilon \kappa^{-1}$ and $\alpha_v = \varepsilon \kappa$ where $\varepsilon > 0$ and $\kappa > 0$ are fixed numeric constants to be given later. 
Our screening test relies on a new formulation of problem~\eqref{sinkhorn-dual}, that we refer as to \emph{approximate dual of Sinkhorn divergence}, given by:

% To construct our appropriate static screening test, the parameters $\alpha_u$ and $\alpha_v$ are expressed via a fixed numeric constants $\varepsilon > 0$ and $\kappa > 0$ to be given later. 
% In spirit of To construct the screening test, we define a new form

\begin{equation} 
\label{screen-sinkhorn}
\min_{u \in \mathcal{C}^n_{\frac \varepsilon \kappa}, v\in \mathcal{C}^m_{\varepsilon\kappa}} \big\{\Psi_{\kappa}(u,v):= \mathbf{1}_n^\top B(u,v)\mathbf{1}_m - \inr{\kappa u, \mu} - \inr{\frac v\kappa, \nu} \big\},
\end{equation}

% Since the objective function $\Psi_{\kappa}$ is convex with respect to $(u,v)$, the set of optima of problem~\eqref{screen-sinkhorn} is non empty. 
The $\kappa$-parameter plays a role of scaling factor, allowing to get a closed order of the potential variables $e^u$ and $e^v$, while the $\varepsilon$-parameter acts like a threshold for these variables.
Note that the approximate dual of Sinkhorn divergence coincides with the dual of Sinkhorn divergence~\eqref{sinkhorn-dual} in the setting of $\varepsilon=0$ and $\kappa=1$.
As explained above, our static screening test is based on constructing two {active sets} denoted $I_{\varepsilon, \kappa}$ and $J_{\varepsilon, \kappa}$ throughout the dual problem of~\eqref{screen-sinkhorn} as follows: %depended on $\varepsilon, \kappa$ and

@@

Proof of Lemma~\ref{I_epsilon_kappa_J_epsilon_kappa} is postponed to the supplementary material. It is worth to note that first order conditions applied to $(u^{*}, v^{*})$ ensure that if $e^{u^{*}_i} > \varepsilon\kappa^{-1}$ then $e^{u^{*}_i} (Ke^{v^{*}})_i =  \kappa\mu_i$ and if $e^{v^{*}_j} > \varepsilon\kappa$ then $e^{v^{*}_j} (K^\top e^{u^{*}})_j =  \kappa^{-1}\nu_j$, that correspond to the Sinkhorn marginal conditions~\cite{peyre2019COTnowpublisher} up to the scaling factor $\kappa$.

@@

Recall that the approximate dual of Sinkhorn divergence is defined with respect to $\varepsilon$ and $\kappa$, where its values depend on a priori \emph{fixed number budget of points} from the supports of $\mu$ and $\nu$.
In the sequel, we denote by $n_b \in\{1, \ldots, n\}$ and $m_b\in\{1, \ldots, m\}$ the number budget of points to be given for resolving problem~\eqref{screen-sinkhorn}. More precisely, we change the domain of the objective function $\Psi_\kappa$ from $\R^n \times \R^m$ to $\R^{n_b} \times \R^{m_b}$. %\textbf{dom}\Psi_\kappa =

\begin{wrapfigure}{o}{0.44\textwidth}
\vspace{-15pt}
\centering
\includegraphics[width=0.4\textwidth]{./figs/kappa_epsilon.pdf}%, height=0.2\textwidth
\caption{Convergence of $(\varepsilon, \kappa)$ to $(0,1)$ as $(n_b,m_b)$ tends to $(n,m)$ for the same setting as in Figure~\eqref{fig:motivations}.}
\label{fig:kappa_epsilon}
\vspace{-15pt}
\end{wrapfigure}

In this spirit, let us define $\xi \in \R^n$ and $\zeta \in \R^m$ to be the ordered decreasing vectors of $\mu \oslash r(K)$ and $\nu \oslash c(K)$ respectively, that is $\xi_1 \geq \xi_2 \geq \cdots \geq \xi_n$ and $\zeta_1 \geq \zeta_2 \geq \cdots \geq \zeta_m$.
To keep only $n_b$-budget and $m_b$-budget of points, the parameters $\kappa$ and $\varepsilon$ satisfy ${\varepsilon^2}\kappa^{-1} = \xi_{n_b}$ and $\varepsilon^2\kappa = \zeta_{m_b}$. Hence 
\begin{equation}
\label{epsilon_kappa}
 \varepsilon = (\xi_{n_b}\zeta_{m_b})^{1/4} \text{ and } \kappa = \sqrt{\frac{\zeta_{m_b}}{\xi_{n_b}}}.
\end{equation}
Note that in one hand we have $|I_{\varepsilon, \kappa}| = n_b$ and $|J_{\varepsilon, \kappa}| = m_b$ by construction. On the other hand, $(n_b,m_b)$ tends to the full number budget of points $(n,m)$, and the couple parameters $(\varepsilon, \kappa)$ tends to $(0,1)$ (see Figure~\ref{fig:kappa_epsilon}), which corresponds to the dual of Sinkhorn divergence~\eqref{sinkhorn-dual}.

Using the previous analysis, any solution $(u^*, v^*)$ of problem~\eqref{screen-sinkhorn} satisfy $e^{u^*_i} \geq \varepsilon\kappa^{-1}$ and $e^{v^*_j} \geq \varepsilon\kappa$ for all $(i,j) \in (I_{\varepsilon,\kappa}\times J_{\varepsilon,\kappa}),$ and $e^{u^*_i} = \varepsilon\kappa^{-1}$ and $e^{v^*_j} = \varepsilon\kappa$ for all $(i,j) \in (I^\complement_{\varepsilon,\kappa}\times J^\complement_{\varepsilon,\kappa})$.
Basing on that facts we restrict the constraints feasibility $\mathcal{C}^n_{\frac \varepsilon \kappa} \cap \mathcal{C}^m_{\varepsilon\kappa}$ to the screened domain defined by $\mathcal{U}_{\text{sc}} \cap \mathcal{V}_{\text{sc}}$ where 
\begin{equation*}
\mathcal{U}_{\text{sc}} = \{u \in \R^{n_b}: e^{u_{I_{\varepsilon,\kappa}}} \succeq \frac \varepsilon\kappa\mathbf 1_{n_b}\} \text{ and } \mathcal{V}_{\text{sc}} =\{v\in\R^{m_b}: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}.%, \text{ and } e^{u_{I^\complement_{\varepsilon,\kappa}}} = \frac\varepsilon\kappa\mathbf 1_{n - n_b}\},
\end{equation*}
% and 
% \begin{equation*}
% 	\mathcal{V}_{\text{sc}} =\{v\in\R^m: e^{v_{J_{\varepsilon,\kappa}}} \succeq \varepsilon\kappa \mathbf{1}_{m_b}\}. %, \text{ and } e^{v_{J^\complement_{\varepsilon,\kappa}}} = \varepsilon\kappa \mathbf 1_{m- m_b}\}.
% \end{equation*}
where the vector comparison $\succeq$ has to be understood elementwise.
Now, we are ready to define the \emph{screened dual of Sinkhorn divergence} as
\begin{align}
\label{screen-sinkhorn_second_def}
\min_{u \in \mathcal{U}_{\text{sc}}, v \in \mathcal{V}_{\text{sc}}}\{\Psi_{\varepsilon, \kappa}(u,v)\}
\end{align}
where 
\begin{align*} 
\Psi_{\varepsilon,\kappa}(u, v) &= (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v_{J_{\varepsilon,\kappa}}} + 
\varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\mathbf 1_{m_b} + \varepsilon \kappa^{-1} \mathbf 1_{n_b}^\top K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}}. %+ \Xi
\end{align*}
%with $\Xi = \varepsilon^2 \sum_{i \in I^\complement_{\varepsilon,\kappa}, j \in J^\complement_{\varepsilon,\kappa}} K_{ij} -\kappa \log(\varepsilon\kappa^{-1})\sum_{i \in I^\complement_{\varepsilon,\kappa}}\mu_i - \kappa^{-1} \log(\varepsilon\kappa)\sum_{j\in J^\complement_{\varepsilon,\kappa}} \nu_j$.

Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradients, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
The L-BFGS-B solver handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
The following lemma (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.

\begin{lemma}
\label{lemma_bounds_of_usc_and_vsc}
Let $(u^{\text{sc}}, v^{\text{sc}})$ be an optimal solution of problem~\eqref{screen-sinkhorn_second_def}, and $K_{\min} = \min\limits_{i\in I_{\varepsilon,\kappa},j \in J_{\varepsilon,\kappa}}K_{ij}$. Then,
one has
\begin{equation}
\label{bound_on_u}
\frac \varepsilon\kappa \vee \frac{\min_{i \in I_{\varepsilon,\kappa}}\mu_i}{\varepsilon (m- m_b) + \varepsilon \vee \frac{\max_{j\in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon\kappa K_{\min}} m_b} \leq e^{u^{\text{sc}}_i} \leq \frac \varepsilon\kappa\vee \frac{\max_{i \in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min}},
\end{equation}
and
\begin{equation}
\label{bound_on_v}
\varepsilon\kappa \vee \frac{\min_{j \in J_{\varepsilon,\kappa}}\nu_j}{\varepsilon(n- n_b) + \varepsilon \vee \frac{\kappa\max_{i\in I_{\varepsilon,\kappa}} \mu_i}{m\varepsilon K_{\min} } n_b} \leq e^{v^{\text{sc}}_j} \leq \varepsilon\kappa \vee \frac{\max_{j \in J_{\varepsilon,\kappa}} \nu_j}{n\varepsilon K_{\min} }
\end{equation}
for all $i\in I_{\varepsilon,\kappa}$ and $j\in J_{\varepsilon,\kappa}$.
\end{lemma}

@@

% \nl   $K_{\min} \gets \min_{i \in I_{\varepsilon,\kappa}, j \in J_{\varepsilon,\kappa}}K_{ij};$ \\
\nl   $\underline{\mu} \gets \min_{i \in I_{\varepsilon,\kappa}} \mu_i, \bar{\mu} \gets \max_{i \in I_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{\nu} \gets \min_{j \in J_{\varepsilon,\kappa}} \mu_i, \bar{\nu} \gets \max_{j \in J_{\varepsilon,\kappa}} \mu_i$; \\
\nl   $\underline{u} \gets \log\big(\frac \varepsilon\kappa \vee \frac{\underline{\mu}}{\varepsilon (m-m_b) + \varepsilon \vee \frac{\bar{\nu}}{n\varepsilon\kappa K_{\min}} m_b}\big), \bar{u} \gets  \log\big(\frac \varepsilon\kappa\vee \frac{\bar{\mu}}{m\varepsilon K_{\min}}\big);$\\
\nl   $\underline{v} \gets \log\big(\varepsilon\kappa \vee \frac{\underline{\nu}}{\varepsilon(n-n_b) + \varepsilon \vee \frac{\kappa\bar{\mu}}{m\varepsilon K_{\min}} n_b}\big), \bar{v} \gets \log\big(\varepsilon\kappa \vee \frac{\bar{\nu}}{n\varepsilon K_{\min}}\big);$\\
\nl   $ \bar{\theta} \gets \text{stack}(\bar{u}\mathbf 1_{n_b}, \bar{v}\mathbf 1_{m_b});$\\
\nl   $ \underline{\theta} \gets \text{stack}(\underline{u}\mathbf 1_{n_b}, \underline{v}\mathbf 1_{m_b}) ;$\\ %\in \R^{n_b\times m_b}

\noindent \textbf{step 2:} \textcolor{black}{L-BFGS-B}\\

\nl  $u^{(0)} \gets \log(\varepsilon\kappa^{-1}) \mathbf 1_{n_b} ;$\\
\nl  $v^{(0)} \gets \log(\varepsilon\kappa) \mathbf 1_{m_b} ;$\\
\nl  $\theta^{(0)} \gets \text{stack}[u^{(0)}, v^{(0)}];$\\
\nl   $\theta \gets \text{L-BFGS-B}(\theta^{(0)}, \underline{\theta}, \bar{\theta});$\\
\nl   $\theta_u \gets (\theta_1, \ldots, \theta_{n_b})^\top, \theta_v \gets(\theta_{n_b+1}, \ldots, \theta_{n_b+m_b})^\top;$\\
